\documentclass[
	ngerman,
	xcolor=dvipsnames,
	11pt
	]{beamer}
\usepackage{babel}
\usepackage[utf8]{inputenc}
\usepackage[LY1]{fontenc}
\renewcommand{\rmdefault}{NexusSerifPro}
\renewcommand{\sfdefault}{NexusSansPro}
%\usepackage{soul}	%\textst command
\usepackage{ulem} 	%\uline \sout \xout \uuline \uwave

\usepackage{tikz}
\usetikzlibrary{arrows,calc}
\tikzset{
%Define standard arrow tip
>=stealth',
%Define style for different line styles
help lines/.style={dashed, thick},
axis/.style={<->},
important line/.style={thick},
connection/.style={thick, dotted},
}

\newcommand{\beginbackup}{
   \newcounter{framenumbervorappendix}
   \setcounter{framenumbervorappendix}{\value{framenumber}}
}
\newcommand{\backupend}{
   \addtocounter{framenumbervorappendix}{-\value{framenumber}}
   \addtocounter{framenumber}{\value{framenumbervorappendix}} 
}

\setbeamertemplate{navigation symbols}{}

%% TUBS
\usetheme[pageofpages=von,% page count separator
          tulogo=tubs,
			 institutelogo=ida]
			 {TUBS}
\usecolortheme{tubs}

\title[ShortTitle]{Corporate Design Template}
\author{Johannes Schlatow}
\institute{}
\date{\today}
\subtitle{\today , My Name}

%\AtBeginSubsection[]
%{
%  \begin{frame}<beamer>
%    \frametitle{Layout}
%    \tableofcontents[currentsection,currentsubsection]
%  \end{frame}
%}

\newenvironment{annot}{\begin{block}{}}{\end{block}}

\begin{document}

\begin{frame}[t,plain]
	\titlepage
\end{frame}

%\frame{\tableofcontents}
\begin{frame}
	\frametitle{Motivation}
\begin{annot}
	This is a simple framed box.
\end{annot}

And some keywords \ldots
\begin{description}
	\item \ldots Auslöser
	\item \ldots Symptome
	\item \ldots Ursachen
	\item \ldots Dynamik
\end{description}
\end{frame}

\section{Chapter 1}
\subsection{Subsection 1}
\begin{frame}
	\frametitle{Topic 1}

	\begin{columns}[t]
		\column{.5\textwidth}
		\begin{block}{Box left}
			\begin{itemize}
				\item Item 1
				\item Item 2
				\item Item 3
				\item Item 4
			\end{itemize}
		\end{block}
		\pause

		\column{.5\textwidth}
		\begin{block}{Box right}
			\begin{itemize}
				\item Item 1
				\item Item 2
				\item Item 3
				\item Item 4
				\item Item 5
			\end{itemize}
		\end{block}
	\end{columns}
\end{frame}

\subsection{Subsection 2}
\begin{frame}
	\frametitle{Topic 2}
	\begin{alertblock}{Attention}
		This is something really important.
		$\Rightarrow$ Take care of it.
	\end{alertblock}
\end{frame}

\section{Chapter 2}
\begin{frame}
	\frametitle{Topic 3}	

	\begin{columns}[t]
		\begin{column}{.5\textwidth}
			\begin{exampleblock}<1->{Example 1}
				Add some text.
			\end{exampleblock}

			\begin{exampleblock}<2->{Example 2}
				Add another text.
			\end{exampleblock}	
		\end{column}
	
		\begin{column}{.5\textwidth}
			\begin{exampleblock}<3->{Example 3}
				More text here.
			\end{exampleblock}

			\begin{exampleblock}<4->{Example 4}
				Last but not least.
			\end{exampleblock}
		\end{column}
	\end{columns}
\end{frame}


\section{Appendix}

\beginbackup
\begin{frame}
	\frametitle{Backup topic 1}
	This is a backup slide. Take a look at the page numbering ;)
\end{frame}

\backupend

\end{document}
